Decentralized Data Marketplace to Enable Trusted Machine Economy

### 2019-09-01 paper.tex
Fix wording
Clean up
Fix wording on DaaS

% to typeset URLs, URIs, and DOIs
\usepackage[english]{babel}
\usepackage{url}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{url,hyperref,graphicx,float,times}
\usepackage{textcomp}
\usepackage{cite}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{amsmath}
\graphicspath{ {./images/} }

\begin{document}
%
\title{Decentralized Data Marketplace to Enable Trusted Machine Economy}
%
\author{
%%% Fill in name here
\IEEEauthorblockN{Zan-Jun Wang\IEEEauthorrefmark{3}, Ching-Hua Lin\IEEEauthorrefmark{2}, Yang-Hao Yuan\IEEEauthorrefmark{4}, Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}}\\

%%% Fill in school here
\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Department of Computer Science and Information Engineering, National Cheng Kung University} \\
\IEEEauthorblockA{\IEEEauthorrefmark{3}Department of Computer Science and Information Engineering, National Taiwan University} \\
\IEEEauthorblockA{\IEEEauthorrefmark{4}BiiLabs, Co., Ltd.} \\

%%% Fill in address here
\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}No.1, University Road, \IEEEauthorrefmark{3}No.1, Sec. 4, Roosevelt Road} \\

%%% Fill in city and country here
\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Tainan City, Taiwan (R.O.C.), \IEEEauthorrefmark{3}Taipei City, Taiwan (R.O.C.)} \\

%%% Fill in email here
\IEEEauthorblockA{\IEEEauthorrefmark{1}jserv@ccns.ncku.edu.tw, \IEEEauthorrefmark{2}jkrvivian@gmail.com, \IEEEauthorrefmark{3}twzjwang@gmail.com, \IEEEauthorrefmark{4}yanghau@biilabs.io}
}

%

\maketitle              
% 50-80 words
\begin{abstract}
Data as a Service (DaaS) offers consumption data, geographic information, etc., for a number of years and have come to form a multi-billion dollar industry. But IoT cannot be considered a mere extension of DaaS. Transacting IoT data must be different in many respects in order to build much-needed trust in IoT-enabled Data Marketplaces, trust that will be key to their sustainability. Data generated internally to an organization is usually not enough to remain competitive, enhance customer experience, and improve strategic decision-making.

@@

% 3 - 4 keywords
\begin{IEEEkeywords}
streaming data, crowd sensing, data marketplace, decentralization
\end{IEEEkeywords}

@@

Take the use case of Airbox\cite{LASS} for instance. Every household with Airbox can collect air quality records automatically and autonomically, rather than passively accept the outcomes from the centralized authorities. To protect privacy, data should be encrypted before on-chain. As for the data reliability, BiiLabs designs the smart-contract-oriented structure to write down every transaction. At the same time, data on-chain will send a verifiable request to mark itself as "being tradeable." This step enables buyers to review and bargain at will. Last but not least, payments will be stored on the smart contracts until the transactions are confirmed. The whole sequence is illustrated in Figure \ref{fig:airbox}.

>>>>

\usepackage[english]{babel}
\usepackage{url}
\usepackage{multicol}
\usepackage{multirow}
\usepackage{url,hyperref,graphicx,float,times}
\usepackage{textcomp}
\usepackage{cite}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{amsmath}
\graphicspath{ {./images/} }

\begin{document}
\title{Decentralized Data Marketplace to Enable Trusted Machine Economy}
\author{
\IEEEauthorblockN{Zan-Jun Wang\IEEEauthorrefmark{3}, Ching-Hua Lin\IEEEauthorrefmark{2}, Yang-Hao Yuan\IEEEauthorrefmark{4}, Ching-Chun (Jim) Huang\IEEEauthorrefmark{1}}\\

\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Department of Computer Science and Information Engineering, National Cheng Kung University} \\
\IEEEauthorblockA{\IEEEauthorrefmark{3}Department of Computer Science and Information Engineering, National Taiwan University} \\
\IEEEauthorblockA{\IEEEauthorrefmark{4}BiiLabs, Co., Ltd.} \\

\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}No.1, University Road, \IEEEauthorrefmark{3}No.1, Sec. 4, Roosevelt Road} \\

\IEEEauthorblockA{\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}Tainan City, Taiwan (R.O.C.), \IEEEauthorrefmark{3}Taipei City, Taiwan (R.O.C.)} \\

\IEEEauthorblockA{\IEEEauthorrefmark{1}jserv@ccns.ncku.edu.tw, \IEEEauthorrefmark{2}jkrvivian@gmail.com, \IEEEauthorrefmark{3}twzjwang@gmail.com, \IEEEauthorrefmark{4}yanghau@biilabs.io}
}

\maketitle
\begin{abstract}
Data as a Service (DaaS) offers consumption data, geographic information, etc., for a number of years and has come to form a multi-billion dollar industry. But IoT cannot be considered a mere extension of DaaS. Transacting IoT data must be different in many respects in order to build much-needed trust in IoT-enabled Data Marketplaces, trust that will be key to their sustainability. Data generated internally to an organization is usually not enough to remain competitive, enhance customer experience, and improve strategic decision-making.

@@

\begin{IEEEkeywords}
streaming data, crowd sensing, data marketplace, decentralization
\end{IEEEkeywords}

@@

Take the use case of Airbox\cite{LASS} for instance. Every household with Airbox can collect air quality records automatically and autonomically, rather than passively accept the outcomes from the centralized authorities. To protect privacy, data should be encrypted before on-chain. As for the data reliability, we extended the backbone design of Airbox to interoperate the smart-contract-oriented structure to write down every transaction. At the same time, data on-chain will send a verifiable request to mark itself as "being tradeable." This step enables buyers to review and bargain at will. Last but not least, payments will be stored on the smart contracts until the transactions are confirmed. The whole sequence is illustrated in Figure \ref{fig:airbox}.
